Forecasting Influenza Hospitalizations Using a Bayesian Hierarchical Nonlinear Model with Discrepancy

### 2024-12-13 nonlinear_forecast.tex
update figures and formatting

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Supplementary Material, including data   %%
%% sets and code, should be provided in     %%
%% {supplement} environment with title      %%
%% and short description. It cannot be      %%
%% available exclusively as external link.  %%
%% All Supplementary Material must be       %%
%% available to the reader on Project       %%
%% Euclid with the published article.       %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{supplement}
\stitle{1. Posterior distribution plots for select parameters}
\sdescription{Plots of posterior distributions for parameters in both ILI and hospitalization models}
\end{supplement}
\begin{supplement}
\stitle{2. FluSight forecast competition scoring results}
\sdescription{Flu forecast results with relative weighted interval scoring rule similar to that used in  FluSight}
\end{supplement}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Supplementary Material, including data   %%
%% sets and code, should be provided in     %%
%% {supplement} environment with title      %%
%% and short description. It cannot be      %%
%% available exclusively as external link.  %%
%% All Supplementary Material must be       %%
%% available to the reader on Project       %%
%% Euclid with the published article.       %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{supplement}
Supplement to "Forecasting Influenza Hospitalizations Using a
Bayesian Hierarchical Nonlinear Model with
Discrepancy"\\
1. Additional plots for ILI \& Hospitalization data for select regions, results from simulation study, and 2023-24 flu analysis\\
% \end{supplement}
2. Posterior distribution plots for select parameters\\
% \sdescription{2. Plots of posterior distributions for parameters in both ILI and hospitalization models}
3. FluSight forecast competition scoring results
\end{supplement}
% \begin{supplement}
% \stitle{3. FluSight forecast competition scoring results}
% \sdescription{Flu forecast results with relative weighted interval scoring rule similar to that used in  FluSight}
% \end{supplement}

### 2024-12-13 supplemental.tex
update figures and formatting

\section{ILI \& Hospitalization data for some regions}

@@

\section{Additional results plots from simulation study}

@@

\section{Additional results plots for 2023-24 flu analysis}

>>>>

\section{Additional plots for ILI \& Hospitalization data for select regions,
         results from simulation study, and 2023-24 flu analysis}

@@

% \section{Additional results plots from simulation study}

@@

% \section{Additional results plots for 2023-24 flu analysis}
